Transfer Learning in Visual and Relational Reasoning

### 2020-03-05 Transfer_Learning/eccv_submission/experiments.tex
Final submitted version

\section{Experiments}
\label{sec:experiments}
% \tk{order: CLEVR + baselines without TL, COG + baseline without TL, Feature Transfer-CLEVR/CoGenT, Temporal Transfer - COG, Reasoning Transfer - CLEVR/CoGenT, Reasoning Transfer-COG}

\begin{figure}[b!]
	\centering
	\includegraphics[width=0.5\textwidth]{../img/plots/clevr_baselines.pdf}
	\caption{Comparison of SAMNet to baselines on CLEVR.}
	\label{fig:clevr_baselines}
\end{figure}

@@

@@

\subsection{Performance of SAMNet on CLEVR}
\label{sec:clevr-baseline-compare}
CLEVR images contain objects characterized by a set of attributes (shape, color, size and material). The questions are grouped into 5 categories: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute}.
The CLEVR authors also introduced CLEVR-CoGenT (Constrained Generalization Test), containing 2 variants, CoGenT-A and CoGenT-B, with varying combinations of color-shape attributes.
The colors are partitioned into two complementary families:
Gray, Blue, Brown, Yellow in Family A; and Red, Green, Purple, Cyan in Family B.
The cubes and cylinders take colors from complementary families in each variant with opposite configurations; the spheres can take any color in both variants (see the dataset description in the supplementary material).
As the input domain consist of the set of objects with all attribute values, both variants differ by their marginal distributions $P_S$ and $P_T$.

\cref{fig:clevr_baselines} presents the accuracy achieved by SAMNet when compared to selected state-of-the-art models, namely: Transparency by Design networks (TbD)~\cite{mascharka2018transparency}, Feature-wise Linear Modulation (FiLM)~\cite{perez2018film} and the Program Generator + Execution Engine (PG + EE)~\cite{johnson2017inferring}.
SAMNet reaches a comparable 96.2\% accuracy, with TbD achieving the best score of 98.7\%.

\subsection{Performance of SAMNet on COG}
\label{sec:cog-baseline-compare}

COG dataset contains short videos, with associated questions grouped into 23 categories\footnote{COG also proposes a pointing version of the tasks, which are not considered in this work.}.
COG comes in two variants: Canonical (easy) and Hard, differing mainly on the number of frames in the video (4 vs. 8), the maximum amount of look-back in frame history containing relevant information for reasoning (3 vs. 7), and the number of object distractors present in a given frame (1 vs. 10) (see the dataset description in the supplementary material).
Since the number of task classes is large, we designed a 2-level hierarchy of task groups using the
description of tasks, as shown in~\cref{fig:task-groups}.

\begin{figure}[b!]
	\centering
	\includegraphics[width=0.6\textwidth]{../img/architecture/hierarchy}
	\caption{Hierarchy of Task Groups in the COG dataset.}
	\label{fig:task-groups}
\end{figure}

For groups at the lowest level, we chose the following task classes to be placed in those groups.
Below, substitute each of \textit{Shape} and \textit{Color} for  \uX{} to obtain the task class.
\begin{description}
	\item[Basic:] \textit{Exist}\uX, \textit{Get}\uX{} and \textit{Exist} (5 task classes);
	\item[Obj-Attr:] \emph{SimpleCompare}\uX{} and \textit{AndSimpleCompare}\uX\ (4 task classes);
	\item[Compare:] \textit{Compare}\uX,  \textit{AndCompare}\uX{} \& \textit{Exist}\uX\textit{Of} (6 task classes);
	\item[Spatial:] \textit{ExistSpace}, \textit{Exist}\uX\textit{Space}, and \textit{Get}\uX\textit{Space} (5 task classes);
	\item[Cognitive:] \textit{ExistLastColorSameShape}, \textit{ExistLastShapeSameColor} and \textit{ExistLastObjectSameObject} (3 task classes)
\end{description}

We compared our results with the baseline model introduced in in~\cite{yang2018dataset}, the same paper as the COG dataset.
The most important results are highlighted in~\cref{fig:samnet_cog_detailed}; full comparison can be found in the supplementary material.

For the Canonical variant (top row), we achieve similar accuracies for the majority of tasks (with a total average accuracy of 98.0\%, compared to 97.6\% for the baseline model), with significant improvements (around 13 points) for \textit{AndCompare} tasks.
As these tasks focus on compositional questions referring to two objects, we hypothesize that our model achieves better accuracy due to its ability to selectively pick and store relevant objects from the past frames in its external memory.
For the Hard variant, we achieve a total average accuracy of 96.1\% compared to 80.1\% for the baseline model, demonstrating that our model can adapt to larger number of frames and distractors.
SAMNet improves upon the baseline model on all tasks, with improvements varying from 0.5 to more than 30 points, especially outperforming in the most complex tasks (\textit{AndCompare}\uX, \textit{Compare}\uX).

@@

When training and testing on CoGenT-A, SAMNet performs slightly worse than the other models, matching the results observed in \cref{sec:clevr-baseline-compare}.
When zero-shot testing on CoGenT-B, all models show relatively good performance (around 75\%), which represents nonetheless a drop of 17 points with respect to CoGenT-A.
All models perform better when fine-tuned on CoGenT-B.
However, this process also results in a degradation of performance on CoGenT-A, with SAMNet and TbD showing an ability to limit this drop in accuracy.
While this suggests both models were able to adapt representations for both domains, these representations are not fully disentangled.

>>>>

\section{Experiments}
\label{sec:experiments}

@@

\subsection{Description of the Datasets}
\label{sec:datasets-desc}

CLEVR images contain objects characterized by a set of attributes (shape, color, size and material). The questions are grouped into 5 categories: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute}.
The CLEVR authors also introduced CLEVR-CoGenT (Constrained Generalization Test), containing 2 variants, CoGenT-A and CoGenT-B, with varying combinations of color-shape attributes.
The colors are partitioned into two complementary families:
Gray, Blue, Brown, Yellow in Family A; and Red, Green, Purple, Cyan in Family B.
The cubes and cylinders take colors from complementary families in each variant with opposite configurations; the spheres can take any color in both variants (see the dataset description in the supplementary material).
As the input domain consist of the set of objects with all attribute values, both variants differ by their marginal distributions $P_S$ and $P_T$.

COG dataset contains short videos with associated questions (classification)
grouped into 23 categories\footnote{COG also proposes pointing-type questions, which are not considered here.}.
COG comes in two variants: Canonical (easy) and Hard, differing mainly on the number of frames in the video (4 vs. 8), the maximum amount of look-back in frame history containing relevant information for reasoning (3 vs. 7), and the number of object distractors present in a given frame (1 vs. 10) (see the dataset description in the supplementary material).

\begin{figure}[!t]
	\centering
	\includegraphics[width=0.6\textwidth]{../img/architecture/hierarchy}
	\caption{Hierarchy of Question Categories in the COG dataset.}
	\label{fig:question-groups}
\end{figure}

Since the number of questions categories is large, we designed a 2-level hierarchy  (see~\cref{fig:question-groups})
that groups these categories appropriately using their descriptions. 
For groups at the lowest level, we chose the following question categories to be placed in those groups.
Below, substitute each of \textit{Shape} and \textit{Color} for  \uX{} to obtain the group.
\begin{description}
	\item[Basic:] \textit{Exist}\uX, \textit{Get}\uX{} and \textit{Exist} (5 categories);
	\item[Obj-Attr:] \emph{SimpleCompare}\uX{} and \textit{AndSimpleCompare}\uX{} (4 categories);
	\item[Compare:] \textit{Compare}\uX,  \textit{AndCompare}\uX{} \& \textit{Exist}\uX\textit{Of} (6 categories);
	\item[Spatial:] \textit{ExistSpace}, \textit{Exist}\uX\textit{Space}, and \textit{Get}\uX\textit{Space} (5 categories);
	\item[Cognitive:] \textit{ExistLastColorSameShape}, \textit{ExistLastShapeSameColor} and \textit{ExistLastObjectSameObject} (3 categories)
\end{description}

\subsection{Performance of SAMNet on CLEVR and COG}
\label{sec:baseline-compare}

\begin{figure}[!b]
	\centering
	\includegraphics[width=0.5\textwidth]{../img/plots/clevr_baselines.pdf}
	\caption{Comparison of SAMNet to baselines on CLEVR.}
	\label{fig:clevr_baselines}
\end{figure}

\cref{fig:clevr_baselines} presents the accuracy achieved by SAMNet on CLEVR
when compared to selected state-of-the-art models, namely: Transparency by Design networks (TbD)~\cite{mascharka2018transparency}, Feature-wise Linear Modulation (FiLM)~\cite{perez2018film} and the Program Generator + Execution Engine (PG + EE)~\cite{johnson2017inferring}.
SAMNet reaches a comparable 96.2\% accuracy, with TbD achieving the best score of 98.7\%.

For COG, we compared our results with the baseline model introduced in~\cite{yang2018dataset}, the same paper as the COG dataset.
The most important results are highlighted in~\cref{fig:samnet_cog_detailed}; full comparison can be found in the supplementary material.

@@

For the Canonical variant (top row), we achieve similar accuracies for the majority of categories (with a total average accuracy of 98.0\%, compared to 97.6\% for the baseline model), with significant improvements (around 13 points) for the \textit{AndCompare} category.
As these question categories focus on compositional questions referring to two objects, we hypothesize that our model achieves better accuracy due to its ability to selectively pick and store relevant objects from the past frames in its external memory.
For the Hard variant, we achieve a total average accuracy of 96.1\% compared to 80.1\% for the baseline model, demonstrating that our model can adapt to larger number of frames and distractors.
SAMNet improves upon the baseline model on all categories, with improvements varying from 0.5 to more than 30 points, especially outperforming in the most complex categories (\textit{AndCompare}\uX, \textit{Compare}\uX).

@@

When training and testing on CoGenT-A, SAMNet performs slightly worse than the other models, matching the results observed in \cref{sec:baseline-compare}.
When zero-shot testing on CoGenT-B, all models show relatively good performance (around 75\%), which represents nonetheless a drop of 17 points with respect to CoGenT-A.
All models perform better when fine-tuned on CoGenT-B.
However, this process also results in a degradation of performance on CoGenT-A, with SAMNet and TbD showing an ability to limit this drop in accuracy.
While this suggests both models were able to adapt representations for both domains, these representations are not fully disentangled.

### 2020-03-05 Transfer_Learning/eccv_submission/experiments_reasoning_transfer.tex
Final submitted version

\subsection{Reasoning transfer in CLEVR-CoGenT}
\label{sec:reasoning-transfer-clevr}
In the following experiments, we used CoGent-A only.
Using the question groups defined by the authors, we organized training and testing splits with the goal of measuring whether mastering reasoning for one questions group can help learning others.

@@

We first trained a single SAMNet instance on CoGenT-A and measured its accuracy on each of the task group $t$ separately.
Those results, indicated in \cref{fig:cogent_reasoning_transfer} as ``Train on All'', serve as baselines for the next two sets of experiments.

We next trained and tested 5 SAMNet instances, each on a single task group $t$ (``Train on t only'').
We observe significant accuracy drops (from 18 up to almost 35 points) in all task groups, except for \textit{Query Attribute}.
We hypothesize \textit{Query Attribute} requires mastering visual grounding and recognizing object attributes, as opposed to the other groups which may not enforce it.
Thus, training on \textit{Query Attribute} helps others, whereas without any training on that particular group, SAMNet struggles developing such skill.

Finally, we trained 5 SAMNet instances as follows: for each task group $t$ we trained a single instance on all tasks but $t$, and tested its performance on $t$ only.
As expected, this setup appears challenging, causing severe performance drops, with accuracy on \textit{Count} and \textit{QueryAttribute} dropping to zero.
This stems from the non-overlapping labels spaces of \textit{Count} (digits 0 to 9) and \textit{QueryAttribute} (all attributes names) with the other groups (binary ``yes'' / ``no''). Thus, the model cannot predict these labels in a zero-shot transfer.

%Besides, the zero accuracy on \textit{Count} can also be explained by the fact that it results from the need of totally different reasoning leading to the answer.
%The \textit{QueryAttribute} latter is more interesting, as when mastering e.g.  \textit{Exist} of  \textit{CompareAttribute} the model \textit{had} to develop some kind of understanding object attributes.
%Still, this result once again suggests that the model learned joint representation of object attributes and struggle with disentangling them without being explicitly trained on task facilitationg that (like the  \textit{QueryAttribute}).

% An additional set of experiments, for which results are available in the supplementary material, fine-tune the model trained on all tasks on each task $t$ respectively.
%Fine-tuning did not demonstrate a clear benefit (except for \textit{Count}, where the accuracy increased by 1.5 pt) without hurting performance on the other tasks. Nevertheless, these experiments leave open the possibility that joint training of tasks may potentially benefit from using weighted sampling towards the tail end with more emphasis on samples from less performing task groups, similar to~\cite{guo2018dynamic, kendall2018multi}.

\subsection{Reasoning transfer in COG Canonical}
\label{sec:reasoning-transfer-cog}
In order to further investigate whether reasoning transfer is effective in leveraging information gained by training a task family at a higher level of the hierarchy, we also conducted a set of experiments using the Canonical variant of COG.
The order of the performed experiments is analogical to the one in the previous section.
The first column (\cref{fig:cog_reasoning_transfer}, ``Train on All'') is taken as a reference, i.e.
we train a single SAMNet instance on all tasks and test on each of the five task groups from the task hierarchy presented in \cref{fig:task-groups}.
Please note that these results are weighted averages of the accuracies of our model on the Canonical variant tasks (\cref{fig:samnet_cog_detailed}).

@@

Next, we experimented with the ``Train on t only'' setup, i.e. training and testing each of 5 SAMNet instances on a single task group $t$ (i.e. the leaves of the proposed hierarchy).
For \textit{Basic}, \textit{Spatial} and \textit{Obj-Attr}, the accuracy is matching the reference (``Train on All''), suggesting that each group contains sufficient information for developing all necessary skills.
Therefore, models trained on these groups may not benefit from any additional training on other task groups.
However, accuracy on \textit{Compary} and \textit{Cognitive} dropped, suggesting the contrary.

Therefore, we have performed a final set of experiments (``Train on Group A/B''), where we trained two SAMNet instances: a) trained on all tasks from \textit{Group A} and tested on each task from the lowest groups (i.e. \textit{Basic}, \textit{Obj-Attr} and \textit{Compare}) separately; b) trained on all tasks from \textit{Group B} and tested separately on \textit{Spatial} and \textit{Cognitive}.
As expected, training on the other tasks from \textit{Group A} enabled the model to significantly improve on the \textit{Compare} task (from 58.6\% to 92.3\%).
A similar improvement (from 68.8\% to 97.1\%) was observed in the second experiment, when trained on \textit{Group B} and tested on \textit{Cognitive}.
Moreover, the achieved accuracy is in fact higher by 1.4 point than the one achieved when training on all tasks (95.7\%).
This suggests the model may have lacked capacity to master questions from all tasks and that training on a smaller subset allowed better performance on this subset.
Finally, we can interestingly note for \textit{Obj-Attr} and \textit{Spatial} that training on the group A/B does not appear to help. When comparing with ``Train on t only'', we observe slight accuracy drops (around 0.3-0.5 point).
Understanding this phenomenon warrants further investigations on the dependencies between the reasoning required by the particular questions and the transferred reasoning.

%With \textbf{Spatial}, we see a small improvement showing that there is some benefit due to joint training with other task families.
%To further emphasize this behavior, notice that just joining \textbf{Compare} with \textbf{Obj-Attr} and \textbf{Basic} already causes a significant accuracy jump to 92.3\%.
%In hindsight, this is not surprising, as the questions in \textbf{Compare} are composed of fragments of questions given by \textbf{Basic} and \textbf{Obj-Attr}, and therefore can leverage the reasoning strategies developed there to reason about questions in \textbf{Compare}.
% Lastly, for the \textbf{Spatial} family, we again see the benefits of joint training with all questions (68.6\% to 95.7\%) but in this case there is a slight loss incurred by including everything. As seen in the figure, just jointly training with \textbf{Spatial} alone is sufficient to get a boost in accuracy (97.1\%). To summarize, while joint training helps, one needs to determine how much of correlation is present with the other tasks.

>>>>

\subsection{Reasoning transfer in CLEVR-CoGenT}
\label{sec:reasoning-transfer-clevr}
In the following experiments, we used CoGent-A only.
Using the question categories defined by the authors, we organized training and testing splits with the goal of measuring whether mastering reasoning for one question category can help learning others.

@@

We first trained a single SAMNet instance on CoGenT-A and measured its accuracy on each of the question category $t$ separately.
Those results, indicated in \cref{fig:cogent_reasoning_transfer} as ``Train on All'', serve as baselines for the next two sets of experiments.

We next trained and tested 5 SAMNet instances, each on a single question category $t$ (``Train on $t$ only'').
We observe significant accuracy drops (from 18 up to almost 35 points) in all question categories, except for \textit{Query Attribute}.
We hypothesize \textit{Query Attribute} requires mastering visual grounding and recognizing object attributes, as opposed to the other groups which may not enforce it.
Thus, training on \textit{Query Attribute} helps others, whereas without any training on that particular group, SAMNet struggles developing such skill.

Finally, we trained 5 SAMNet instances as follows: for each category $t$, we trained a single instance on all categories but $t$, and tested its performance on
category $t$ only.
As expected, this setup appears challenging, causing severe performance drops, with accuracy on \textit{Count} and \textit{QueryAttribute} dropping to zero.
This stems from the non-overlapping labels spaces of \textit{Count} (digits 0 to 9) and \textit{QueryAttribute} (all attributes names) with the other groups (binary ``yes'' / ``no''). Thus, the model cannot predict these labels in a zero-shot transfer.

\subsection{Reasoning transfer in COG Canonical}
\label{sec:reasoning-transfer-cog}
In order to further investigate whether reasoning transfer is effective in leveraging information gained by training a question group at a higher level of the hierarchy, we also conducted a set of experiments using the Canonical variant of COG.
The order of the performed experiments is analogical to the one in the previous section.
The first column (\cref{fig:cog_reasoning_transfer}, ``Train on All'') is taken as a reference, i.e.
we train a single SAMNet instance on all questions and test on each of the five question groups from the hierarchy shown in~\cref{fig:question-groups}.
Note that these results are weighted averages of accuracies of our model on the Canonical variant (\cref{fig:samnet_cog_detailed}).

@@

Next, we experimented with the ``Train on $t$ only'' setup, i.e. training and testing each of 5 SAMNet instances on a single question group $t$ (i.e. the leaves of the proposed hierarchy).
For \textit{Basic}, \textit{Spatial} and \textit{Obj-Attr}, the accuracy is matching the reference (``Train on All''), suggesting that each group contains sufficient information for developing all necessary skills.
Therefore, models trained on these groups may not benefit from any additional training on other question groups.
However, accuracy on \textit{Compary} and \textit{Cognitive} dropped, suggesting the contrary.

Therefore, we performed a final set of experiments (``Train on Group A/B''), where we trained two SAMNet instances: a) trained on all questions from \textit{Group A} and tested on each of the lowest groups below \textit{Group A}, i.e. \textit{Basic}, \textit{Obj-Attr} and \textit{Compare}, separately; b) trained on all questions from \textit{Group B} and tested separately on \textit{Spatial} and \textit{Cognitive} groups.
As expected, training on the other questions from \textit{Group A} enabled the model to significantly improve on the \textit{Compare} category (from 58.6\% to 92.3\%).
A similar improvement (from 68.8\% to 97.1\%) was observed in the second experiment, when trained on \textit{Group B} and tested on \textit{Cognitive}.
Moreover, the achieved accuracy is in fact higher by 1.4 point than the one achieved when training on all questions (95.7\%).
This suggests the model may have lacked capacity to master questions from all questions and that training on a smaller subset allowed better performance on this subset.
Finally, we can interestingly note for \textit{Obj-Attr} and \textit{Spatial} that training on the Group A/B does not appear to help. When comparing with ``Train on $t$ only'', we observe slight accuracy drops (around 0.3-0.5 point).
Understanding this phenomenon warrants further investigations on the dependencies between the reasoning required by the particular questions and the transferred reasoning.

### 2020-03-05 Transfer_Learning/eccv_submission/transfer_learning.tex
Final submitted version

A \emph{domain} is a pair $\cD = (\cX,P(X))$, where $\cX$ is a feature space and $P(X)$ is a probability distribution on $\cX$.
For visual reasoning problems considered in this paper,
$\cX$ will consist of purely visual inputs, i.e., either images or videos in some cases, or
a combination of both visual inputs and questions in other cases.
A \emph{task} is a pair $\cT= (\cY,f(\cdot))$, where $\cY$ is a label space and $f: \cX \to \cY$ is a prediction function.
When the domain elements consist of both the question and the visual input, there is only one task, namely, to answer the
question\footnote{% 
	For the COG dataset, the answer is a tuple, one for each frame in the video, whereas typical video answering datasets only require a single answer for the entire video.}.
If the domain elements consist of just the visual inputs, then the task is further parameterized the question so that each question
defines a separate task.

\begin{definition}[\cite{pan2009survey}]
	\label{defn:transfer}
	Given a source domain $\cD_S$ and a source learning task $\cT_S$, a target domain $\cD_T$ and a target learning task $\cT_T$, transfer learning aims to help improve the
	learning of the target predictive function $f_T(\cdot)$ in $\cD_T$ using the knowledge  in $\cD_S$ and $\cT_S$, where $\cD_S \ne \cD_T$, or $\cT_S \ne \cT_T$.
\end{definition}
In this paper, we study the setting of \emph{domain adaptation}
where $\cT_S \ne \cT_T$ and $\cX_S = \cX_T$, so $\cD_S \ne \cD_T$ means that the distributions $P_S$ and $P_T$ are different.

\Cref{defn:transfer} is quite general but does not give a nuanced view of different aspects of visual reasoning.
As mentioned in the introduction, one setting is the case of static images,
where this could be due to having different feature combinations in the source and target.
A different setting is in the context of video reasoning where the number of frames can increase significantly going from source to target.
These require possibly very different methods: the first involves building disentangled feature representations that can generalize across
domains; the second might need external memory to remember relevant objects to generalize across frame lengths.
Another situation is when the questions themselves can be grouped into families such as count-based queries,
comparison of objects, or existence of objects with certain features etc.
This entails studying transfer learning in specific settings.

@@

We now formally define 3 kinds of transfer learning problems, namely,
\emph{feature transfer}, \emph{temporal transfer},
and \emph{reasoning transfer}.
These are illustrated in~\cref{fig:taskonomy} using representative examples from CLEVR using dataset variants CoGenT-A and CoGenT-B, and COG using two dataset types: canonical and hard. These datasets were chosen because they
are particularly suited for experimental investigations of transfer learning described in the following section.
%In \cref{sec:experiments}, we detail the performance of SAMNet for each of these 3 kinds, using the CLEVR-CoGenT dataset for feature transfer, the COG dataset for temporal transfer, and finally both datasets for reasoning transfer, with appropriate baseline comparisons.
Let $\cQ$ and $\cV$ denote the set of questions and visual inputs, respectively.
\begin{description}
	%\compresslist % used to reduce spacing
	\item[Feature Transfer:] In this setting of domain adaptation, $\cX_S = \cX_T \subseteq \cQ \times \cV$
	and the task $f(q,v)$ is just the answer to the question $q$ on visual input $v$. The output set $\cY$ is the union of legitimate answers
	over all questions in $\cQ$.
	The distributions $P_S$ and $P_T$ differ in the feature attributes such as shape, color, and size, or their combinations
	thereof.
	For example, CoGenT-A and CoGenT-B variants of CLEVR use complementary colors
	for cubes and cylinders (\cref{fig:taskonomy}), so $P_S$ and $P_T$ have disjoint support when conditioned on these shapes. This is empirically investigated in~\cref{sec:feature}.

	\item[Temporal Transfer:] This is again similar to feature transfer in that $\cX_S = \cX_T \subseteq \cQ \times \cV$
	and there is a single task.	The key difference is that we introduce a complexity measure $C(q,v)$ that reflects the ease or difficulty of answering question $q$ on visual input $v$. 
	For any $(q_S,v_S)$ and $(q_T,v_T)$ in the support of $P_S$ and $P_T$ respectively, we require that $C(q_S,v_S)$ is strictly less than $C(q_T,v_T)$.
	For example, going from the COG canonical dataset to the hard dataset, we see that there are more distracting objects in each frame and more frames to process that could cumulatively affect the ability to transfer the learned model for the canonical dataset to the hard version. This is empirically investigated in~\cref{sec:temporal}.

	\item[Reasoning Transfer:]
	Here, we investigate whether reasoning processes can be transferred in the setting where questions in the source and target domain belong to different categories.
	A \emph{task family} is defined by a fixing subset of $\cQ$ that share common traits.
	\Cref{fig:taskonomy} shows representative questions for two task families: \textit{CompareColor} and \textit{AndCompareColor}.
	Given a fixed global distribution on $\cQ \times \cV$, this induces a marginal distribution for each task family.
	Let $\cF_S$ be the source task family and $\cF_T$ be the target task family.
	In typical cases of transfer learning, $\cF_S$ and $\cF_T$ will involve disjoint sets of tasks and therefore, the support of $P_S$ and $P_T$ of the induced distribution on $\cQ \times \cV$ will also be disjoint.
	In such cases, transfer learning is most effective when the two categories share common attributes in the reasoning process. This is evident in the case of \textit{CompareColor} and \textit{AndCompareColor} where the latter task, despite being complex, involves reasoning elements that can be found in the former task. The effectiveness of reasoning transfer with respect to various combinations of source-target pairs is thoroughly investigated in~\cref{sec:reasoning-transfer-clevr} using the CoGenT-A variant of CLEVR and in~\cref{sec:reasoning-transfer-cog} using the COG canonical dataset.

>>>>

A \emph{domain} is a pair $\cD = (\cX,P(X))$, where $\cX$ is a feature space and $P(X)$ is a probability distribution on $\cX$.
For visual reasoning problems considered in this paper, the feature space
$\cX$ is some appropriate subset of the Cartesian product of visual inputs and questions.
A \emph{task} is a pair $\cT= (\cY,f(\cdot))$, where $\cY$ is a label space and $f: \cX \to \cY$ is a prediction function.
For visual reasoning, the task is simply to answer the
given question on the given visual input\footnote{% 
	For the COG dataset, the answer is a tuple, one for each frame in the video, whereas typical video answering datasets only require a single answer for the entire video.}.

\begin{definition}[\cite{pan2009survey}]
	\label{defn:transfer}
	Given a source domain $\cD_S$ and a source learning task $\cT_S$, a target domain $\cD_T$ and a target learning task $\cT_T$, transfer learning aims to help improve the
	learning of the target predictive function $f_T(\cdot)$ in $\cD_T$ using the knowledge  in $\cD_S$ and $\cT_S$, where $\cD_S \ne \cD_T$, or $\cT_S \ne \cT_T$.
\end{definition}
In this paper, we study the setting of \emph{domain adaptation}
where $\cT_S = \cT_T$ and $\cX_S = \cX_T$, so $\cD_S \ne \cD_T$ means that the distributions $P_S$ and $P_T$ are different.

\Cref{defn:transfer} is quite general but does not give a nuanced view of 
the different aspects of visual reasoning.
As mentioned in the introduction, one setting is the case of static images,
where this could be due to having different feature combinations in the source and target.
A different setting is in the context of video reasoning where the number of frames can increase significantly going from source to target.
These require possibly very different methods: the first involves building disentangled feature representations that can generalize across
domains; the second might need external memory to remember relevant objects to generalize across frame lengths.
Another situation is when the questions themselves can be grouped into families such as count-based queries,
comparison of objects, or existence of objects with certain features etc.
This motivates studying transfer learning for visual reasoning using a more detailed approach.

@@

We now formally define 3 kinds of transfer learning problems for visual reasoning, 
namely, \emph{feature transfer}, \emph{temporal transfer}, and \emph{reasoning transfer}.
These are illustrated in~\cref{fig:taskonomy} using representative examples from CLEVR using dataset variants CoGenT-A and CoGenT-B, and COG using two dataset types: canonical and hard. These datasets were chosen because they
are particularly suited for experimental investigations of transfer learning described in the following section.
%In \cref{sec:experiments}, we detail the performance of SAMNet for each of these 3 kinds, using the CLEVR-CoGenT dataset for feature transfer, the COG dataset for temporal transfer, and finally both datasets for reasoning transfer, with appropriate baseline comparisons.
Let $\cQ$ and $\cV$ denote the set of questions and visual inputs, respectively.
The feature space is $\cQ \times \cV$ and the task is to answer
the question $q \in \cQ$ on visual input $v \in \cV$.
The output set $\cY$ is the union of legitimate answers
over all questions in $\cQ$.
\begin{description}
	%\compresslist % used to reduce spacing
	\item[Feature Transfer:] In this setting of domain adaptation, 
	the distributions $P_S$ and $P_T$ of the source and target, respectively, differ in the feature attributes such as shape, color, and size, or their combinations
	thereof.
	For example, CoGenT-A and CoGenT-B variants of CLEVR use complementary colors
	for cubes and cylinders (\cref{fig:taskonomy}), so $P_S$ and $P_T$ have disjoint support when conditioned on these shapes. This is empirically investigated in~\cref{sec:feature}.

	\item[Temporal Transfer:] Here we introduce a complexity measure $C(q,v)$ that reflects the ease or difficulty of answering question $q$ on 
	visual input $v$ that takes the temporal aspect of reasoning into account.
	For any $(q_S,v_S)$ and $(q_T,v_T)$ in the support of $P_S$ and $P_T$ respectively, we require that $C(q_S,v_S)$ is strictly less than $C(q_T,v_T)$.
	For example, going from the COG canonical dataset to the hard dataset, we see that there are more distracting objects in each frame and more frames to process that could cumulatively affect the ability to transfer the learned model for the canonical dataset to the hard version. This is empirically investigated in~\cref{sec:temporal}.

	\item[Reasoning Transfer:]
	Here, we investigate whether the reasoning processes can be transferred in the setting where questions in the source and target domain belong to different categories.
	Fix a subset $\cQ' \subseteq \cQ$ of questions sharing a common structure.
	\Cref{fig:taskonomy} shows representative questions for two subsets with  self-explanatory names: \textit{CompareColor} and \textit{AndCompareColor}.
	Given a fixed global distribution on $\cQ \times \cV$, observe that
	$\cQ'$ induces a conditional distribution on $\cQ \times \cV$.
	Let $\cQ_S$ and $\cQ_T$ be the source and target questions, respectively; typically, $\cQ_S$ and $\cQ_T$ will be disjoint, therefore, this also holds for the support of $P_S$ and $P_T$ on the induced distribution.
	Transfer learning in this setting is most effective when the source and target questions
	share common attributes in the reasoning process. This is evidently true for \textit{CompareColor} and the more complex \textit{AndCompareColor}; the latter category involves reasoning elements that can be found in the former category. The effectiveness of reasoning transfer with respect to various combinations of source-target pairs is thoroughly investigated in~\cref{sec:reasoning-transfer-clevr} using the CoGenT-A variant of CLEVR and in~\cref{sec:reasoning-transfer-cog} using the COG canonical dataset.
